---
title: "Analysis of User SubSequences "
author: "Corey Jackson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, cache=TRUE}
library(readr)
library(dplyr)
library(tabula)
library(gtsummary)
library(ggpubr)
library(reshape2)
library(stringr)
library(data.table)
library(DT)

userW1W2 <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W1W2/Subsequences_Count_W1W2.csv")

userW1W2 <- userW1W2[,-1]
userW1W2_org <- userW1W2


userW1W2 <- userW1W2 %>%
  mutate(total_subsequeces = rowSums(.[1:21])) %>%
  rowwise() %>% 
  mutate(unique_subsequeces = 21- sum(c_across(1:21) == 0))
  
# Measure diversity of activities 
## https://cran.r-project.org/web/packages/tabula/vignettes/diversity.html 
userW1W2 <- data.frame(userW1W2)
userW1W2$Status2 <- ifelse(userW1W2$Status=="Promoted",1,0)

userW1W2$richness <- as.numeric(richness(userW1W2[1:21], method = "margalef")) 
userW1W2_richness <- na.omit(userW1W2) 
wilcox.test(userW1W2_richness$richness,userW1W2_richness$Status2)

userW1W2$rarefaction <- as.numeric(composition(userW1W2[1:21], method = "chao1")) 
userW1W2_rarefaction <- na.omit(userW1W2) 
wilcox.test(userW1W2_rarefaction$rarefaction,userW1W2_rarefaction$Status2)

userW1W2$workflow <- "W1W2"
##################################################################

userW2W3<- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W2W3/Subsequences_Count_W2W3.csv")

userW2W3 <- userW2W3[,-1]
userW2W3_org <- userW2W3

userW2W3 <- userW2W3 %>%
  mutate(total_subsequeces = rowSums(.[1:42])) %>%
  rowwise() %>% 
  mutate(unique_subsequeces = 42 - sum(c_across(1:42) == 0))

userW2W3 <- data.frame(userW2W3)
userW2W3$Status2 <- ifelse(userW2W3$Status=="Promoted",1,0)

userW2W3$richness <- as.numeric(richness(userW2W3[1:42], method = "margalef")) 
userW2W3_richness <- na.omit(userW2W3) 
wilcox.test(userW2W3_richness$richness,userW2W3_richness$Status2)

userW2W3$rarefaction <- as.numeric(composition(userW2W3[1:42], method = "chao1")) 
userW2W3_rarefaction <- na.omit(userW2W3) 
wilcox.test(userW2W3_rarefaction$rarefaction,userW2W3_rarefaction$Status2)

userW2W3$workflow <- "W2W3"
##################################################################

userW3W4 <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W3W4/Subsequences_Count_W3W4.csv")

userW3W4 <- userW3W4[,-1]
userW3W4_org <- userW3W4

userW3W4 <- userW3W4 %>%
  mutate(total_subsequeces = rowSums(.[1:299])) %>%
  rowwise() %>% 
  mutate(unique_subsequeces = 299 - sum(c_across(1:299) == 0))

userW3W4 <- data.frame(userW3W4)
userW3W4$Status2 <- ifelse(userW3W4$Status=="Promoted",1,0)


userW3W4$richness <- as.numeric(richness(userW3W4[1:299], method = "margalef")) 
userW3W4_richness <- na.omit(userW3W4) 
wilcox.test(userW3W4_richness$richness,userW3W4_richness$Status2)

userW3W4$rarefaction <- as.numeric(composition(userW3W4[1:299], method = "chao1")) 
userW3W4_rarefaction <- na.omit(userW3W4) 
wilcox.test(userW3W4_rarefaction$rarefaction,userW3W4_rarefaction$Status2)

userW3W4$workflow <- "W3W4"


##################################################################
userW4W5 <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W4W5/Pt2_Threshold/Subsequences_Count_W4W5.csv")

userW4W5 <- userW4W5[,-1]
userW4W5_org <- userW4W5


userW4W5 <- userW4W5 %>%
  mutate(total_subsequeces = rowSums(.[1:256])) %>%
  rowwise() %>%
  mutate(unique_subsequeces = 256 - sum(c_across(1:256) == 0))

userW4W5 <- data.frame(userW4W5)
userW4W5$Status2 <- ifelse(userW4W5$Status=="Promoted",1,0)


userW4W5$richness <- as.numeric(richness(userW4W5[1:256], method = "margalef"))
userW4W5_richness <- na.omit(userW4W5)
wilcox.test(userW4W5_richness$richness,userW4W5_richness$Status2)

userW4W5$rarefaction <- as.numeric(composition(userW4W5[1:256], method = "chao1"))
userW4W5_rarefaction <- na.omit(userW4W5)
wilcox.test(userW4W5_rarefaction$rarefaction,userW4W5_rarefaction$Status2)

userW4W5$workflow <- "W4W5"

### COMBINE

userworkflows <- rbind(userW1W2[,c(22:29)],userW2W3[,c(43:50)],userW3W4[,c(300:307)],userW4W5[257:264])
#userworkflows <- rbind(userW1W2[,c(22:29)],userW2W3[,c(43:50)],userW3W4[,c(300:307)])

userworkflows_differences <- na.omit(userworkflows)

#Compute change in richness and rarefaction
userworkflows <- userworkflows %>%
    arrange(desc(user),workflow) %>%
    group_by(user) %>%
    mutate(diff_richness = richness - lag(richness),
           diff_rarefaction = rarefaction - lag(rarefaction)
           )


W1W2_summary <-  userworkflows[,c(1,3,4,6,7,8)] %>%
  filter(workflow=="W1W2") %>%
  select(-workflow) %>%
  tbl_summary(by = Status, 
  statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>% 
  add_p()

W2W3_summary <-  userworkflows[,c(1,3,4,6,7,8)] %>%
  filter(workflow=="W2W3") %>%
  select(-workflow) %>%
  tbl_summary(by = Status, 
    statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%   add_p()

W3W4_summary <-  userworkflows[,c(1,3,4,6,7,8)] %>%
  filter(workflow=="W3W4") %>%
  select(-workflow) %>%
  tbl_summary(by = Status, 
   statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%   add_p()

W4W5_summary <-  userworkflows[,c(1,3,4,6,7,8)] %>%
  filter(workflow=="W4W5") %>%
  select(-workflow) %>%
  tbl_summary(by = Status,
   statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%   add_p()

### DIfFERENCES
userworkflows_differences <- na.omit(userworkflows)

W2W3_diff <-  userworkflows_differences[,c(1,8:10)] %>%
  filter(workflow=="W2W3") %>%
  select(-workflow) %>%
 tbl_summary(by = Status, 
  statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%  
  add_p()

W3W4_diff <-  userworkflows_differences[,c(1,8:10)] %>%
  filter(workflow=="W3W4") %>%
  select(-workflow) %>%
  tbl_summary(by = Status, 
  statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%
  add_p()

W4W5_diff <-  userworkflows_differences[,c(1,8:10)] %>%
  filter(workflow=="W4W5") %>%
  select(-workflow) %>%
  tbl_summary(by = Status,
  statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%
  add_p()
```

The higher the number of sequences present, the higher the sequence richness.

## Sequence Richness

The higher the number of sequences present, the higher the sequence richness.

## Sequence Rarefaction

A statistical technique used to compare the sequence richness of different samples that have been collected from different areas or at different times. It is used to estimate the expected number of sequence in a sample of a given size, based on the number of sequence found in a larger sample size. Rarefaction is a tool used to compare the relative richness of different samples, and to estimate the expected number of sequences in a smaller sample size

```{r}
W1W2_summary

W2W3_summary

W3W4_summary

W4W5_summary
```

### Changes in richness and rarefaction

```{r}
W2W3_diff

W3W4_diff

W4W5_diff

```

## Changes in user routines

For each workflow identify which sequences are present


```{r include=FALSE, warning=FALSE, cache=TRUE}

##########################################
################## W1W2 ################## 
##########################################
userW1W2_activities <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W1W2/ConcatSequenceW1W2.csv")
names(userW1W2_activities)[1:2] <- c("user","status")

userW1W2_activities[, 3:dim(userW1W2_activities)[2]][userW1W2_activities[, 3:dim(userW1W2_activities)[2]] == 0] <- NA


melt_userW1W2_activities <- melt(userW1W2_activities, id = c("user","status")) 
remove(userW1W2_activities)

userW1W2_activities <- melt_userW1W2_activities %>%
  group_by(user, status, value) %>%
  summarize(count = n())
userW1W2_activities <- userW1W2_activities[which(!is.na(userW1W2_activities$value)),]
userW1W2_activities$workflow <- "W1W2"
remove(melt_userW1W2_activities)

##########################################
################## W2W3 ################## 
##########################################

userW2W3_activities <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W2W3/ConcatSequenceW2W3.csv")
names(userW2W3_activities)[1:2] <- c("user","status")

userW2W3_activities[, 3:dim(userW2W3_activities)[2]][userW2W3_activities[, 3:dim(userW2W3_activities)[2]] == 0] <- NA


melt_userW2W3_activities <- melt(userW2W3_activities, id = c("user","status")) 
remove(userW2W3_activities)

userW2W3_activities <- melt_userW2W3_activities %>%
  group_by(user, status, value) %>%
  summarize(count = n())
userW2W3_activities <- userW2W3_activities[which(!is.na(userW2W3_activities$value)),]
userW2W3_activities$workflow <- "W2W3"
#remove(melt_userW2W3_activities)
##########################################
################## W3W4 ################## 
##########################################

userW3W4_activities <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W3W4//ConcatSequenceW3W4.csv")
names(userW3W4_activities)[1:2] <- c("user","status")

userW3W4_activities[, 3:dim(userW3W4_activities)[2]][userW3W4_activities[, 3:dim(userW3W4_activities)[2]] == 0] <- NA


melt_userW3W4_activities <- melt(userW3W4_activities, id = c("user","status")) 
remove(userW3W4_activities)

userW3W4_activities <- melt_userW3W4_activities %>%
  group_by(user, status, value) %>%
  summarize(count = n())
userW3W4_activities <- userW3W4_activities[which(!is.na(userW3W4_activities$value)),]
userW3W4_activities$workflow <- "W3W4"
remove(melt_userW3W4_activities)

##########################################
################## W4W5 ################## 
##########################################

userW4W5_activities <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W4W5/ConcatSequenceW4W5.csv")
names(userW4W5_activities)[1:2] <- c("user","status")


userW4W5_activities[, 3:dim(userW4W5_activities)[2]][userW4W5_activities[, 3:dim(userW4W5_activities)[2]] == 0] <- NA


melt_userW4W5_activities <- melt(userW4W5_activities, id = c("user","status")) 
remove(userW4W5_activities)

userW4W5_activities <- melt_userW4W5_activities %>%
  group_by(user, status, value) %>%
  summarize(count = n())
userW4W5_activities <- userW4W5_activities[which(!is.na(userW4W5_activities$value)),]
userW4W5_activities$workflow <- "W4W5"
remove(melt_userW4W5_activities)

activities <-  rbind(userW1W2_activities,userW2W3_activities,userW3W4_activities,userW4W5_activities)
remove(w1_w2_activities,w2_w3_activities, w3_w4_activities,w4_w5_activities)

library(tidyverse)
spread_activities <- activities %>%
  spread(value, count, fill = 0) 
 spread_activities <- arrange(spread_activities, user, workflow)

```


```{r include=FALSE, warning=FALSE, cache=TRUE}
# Sort the dataframe by user and level for accurate comparison
spread_activities <- spread_activities[order(spread_activities$user, as.numeric(spread_activities$workflow)), ]

spread_activities[, 4:14][spread_activities[, 4:14] >= 1] <- 1

# Create a new dataframe to store the number of new activities
new_activities <- data.frame(user = character(), level = character(), new_activities_count = integer(), activities = integer(), stringsAsFactors = FALSE)


# Iterate over each user
users <- unique(spread_activities$user)
for (u in users) {
  # Get the subset of data for the current user
  user_data <- spread_activities[spread_activities$user == u, ]
  # Iterate over each level for the current user
  levels <- unique(user_data$workflow)
  for (lvl in levels) {
    
    # Determine the new activities in the current level
    current_level_data <- user_data[user_data$workflow == lvl, ]
    previous_levels_data <- user_data[user_data$workflow < lvl, ]
    
    # Sum up data in previous_levels_data
    sum <- colSums(previous_levels_data[-c(1:3)])
    previous_activities <-  data.frame(column = names(previous_levels_data)[-c(1:3)], prev = sum)
      
    sums_cur <- colSums(current_level_data[-c(1:3)])
      current_activities <-  data.frame(column = names(current_level_data)[-c(1:3)], curr = sums_cur)
   
      act_sum <- merge(previous_activities,current_activities, by="column")
                                   
    # Identify which columns have 0 in previous 
    newact <- act_sum$column[which(act_sum$prev==0 & act_sum$curr==1)]
    new_activities_count <- length(newact)
    
    new_activities <- rbind(new_activities, 
                            data.frame(user = u, level = lvl, new_activities_count = new_activities_count, activities = paste(newact, collapse = ", "), stringsAsFactors = FALSE))
  }
}


names(spread_activities)[3] <- "level"
spread_activities <- merge(spread_activities,new_activities, by =c("user","level"))


tbl <- 
  spread_activities %>%
  select(level, status, new_activities_count) %>%
  tbl_strata(
    strata = level,
    ~.x %>%
      tbl_summary(
        by = status,
        type = where(is.numeric) ~ "continuous"
      ) %>%
      modify_header(all_stat_cols() ~ "**{level}**")
  )


### BAR CHART SHOWING THE NUMBER OF AVERAGE NUMBER OF NEW ACTIVITIES

### TABLE
lvl_activity_table <- spread_activities %>% 
                    group_by(level, status) %>% 
                    summarise(new_activity =
                                    mean(new_activities_count))

data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE),
      median = median(x[[col]], na.rm=TRUE))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}


df2 <- data_summary(spread_activities, varname="new_activities_count", 
                    groupnames=c("level", "status"))


### VIZ
library("ggsci")

# https://cran.r-project.org/web/packages/ggsci/vignettes/ggsci.html 
lvl_activity_table.viz <- ggplot(df2, aes(x=level, y=new_activities_count, fill=status)) + 
  geom_bar(stat="identity", color="black", 
           position=position_dodge()) +
  geom_errorbar(aes(ymin=new_activities_count-sd, ymax=new_activities_count+sd), width=.2,
                 position=position_dodge(.9)) + 
  labs(x="Workflow", y = "New activities", fill='Status') +
  theme_minimal() + 
  scale_fill_jama() + 
  theme(plot.title = element_text(size=12,face = "bold"),
    legend.position = c(.8, .8),
    legend.key.size = unit(1, 'cm'),
        axis.text = element_text(size=15,face = "bold")
       )

# tests
library(plyr)

# Split df by "sex" and apply function to each subset of df. Returns a list of the return values.
dlply(.data = spread_activities, .variables = "level", .fun = function(x) {
  with(x, wilcox.test(new_activities_count~status))
})

detach("package:plyr")


p <- ggboxplot(spread_activities, x = "status", y = "new_activities_count",
          color = "status", palette = "jama",
          facet.by = "level", short.panel.labs = TRUE) + 
  labs(x="Workflow", y = "New activities", fill='Status') +
  theme_minimal() + 
  scale_fill_jama() + 
  theme(plot.title = element_text(size=12,face = "bold"),
    legend.position = "none",
        axis.text = element_text(size=12,face = "bold")
       )

p <- p + stat_compare_means(method = "wilcox.test", label.x = 1.5, label.y = 9)

#tiff("~/Desktop/Figure 3.tiff", units="cm", width = 30, height = 15, res=300)
#lvl_activity_table.viz
#dev.off()

png("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/cscw-analysis/figures/Figure 3.png", width = 30, height = 15, units = 'cm', res = 300)
lvl_activity_table.viz
dev.off()

png("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/cscw-analysis/figures/Figure 3_alt.png", width = 30, height = 15, units = 'cm', res = 300)
p
dev.off()
```

```{r}
df2

lvl_activity_table.viz

p
```


```{r include=FALSE, warning=FALSE,cache=TRUE}
### Get which activities as a percentage are people invovled in at each level

# Extract user, status, and activities
dataset <- data.frame(user = spread_activities$user,
                      status = spread_activities$status,
                      level = spread_activities$level,
                      activities = spread_activities$activities)

expanded_dataset <- do.call(rbind, lapply(seq_len(nrow(dataset)), function(i) {
  activities <- strsplit(as.character(dataset$activities[i]), ",")[[1]]
  data.frame(
    user = rep(dataset$user[i], length(activities)),
    status = rep(dataset$status[i], length(activities)),
    level = rep(dataset$level[i], length(activities)),
    activities = activities,
    stringsAsFactors = FALSE
  )
}))

library(dplyr)

expanded_dataset$activities <- gsub("[[:space:]]", "", expanded_dataset$activities)

activity_counts <- expanded_dataset %>%
  dplyr::group_by(level, status, activities) %>%
  dplyr::summarize(count = n_distinct(user)) %>%
  dplyr::group_by(level, status) %>%
  dplyr::mutate(total_users = sum(count),
         percentage = count / total_users * 100)

comparison <- activity_counts %>%
  dplyr::ungroup() %>%
  dplyr::group_by(level, activities) %>%
  dplyr::summarize(prop_test = list(prop.test(count, total_users)))

result_df <- comparison %>%
  dplyr::ungroup() %>%
  dplyr::mutate(statistic = sapply(prop_test, function(x) x$statistic),
         p_value = sapply(prop_test, function(x) x$p.value)) %>%
  dplyr::select(level, activities, statistic, p_value)

```

```{r}
datatable(data = activity_counts, caption = "Workflow Activities", filter = "top")
```


```{r}
datatable(data = result_df, caption = "Proportions Test", filter = "top")
```

###
```{r}
library(data.table)
#### Granular sequences
W1W2_geordi <- fread("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W1W2/ConcatSequenceW1W2.csv")

# Melt data
W1W2_geordi.m <- reshape2::melt(W1W2_geordi[-1,], id = c("V1","V2")) 
W1W2_geordi.m <- W1W2_geordi.m[which(W1W2_geordi.m$value !="0"),]
names(W1W2_geordi.m) <- c("user_id","status","order","action") 
W1W2_geordi.m$order <- gsub("V","",W1W2_geordi.m$order)
remove(W1W2_geordi)

W1W2_geordi.usersummary <- W1W2_geordi.m %>%
  select(user_id,status,action) %>%
  group_by(user_id,status,action) %>%
  tally()

W2W3_geordi <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W2W3/ConcatSequenceW2W3.csv")

# Melt data
W2W3_geordi.m <- reshape2::melt(W2W3_geordi, id = c("...1","0")) 
W2W3_geordi.m <- W2W3_geordi.m[which(W2W3_geordi.m$value != "0"),]
names(W2W3_geordi.m) <- c("user_id","status","order","action") 
W2W3_geordi.m$order <- gsub("V","",W2W3_geordi.m$order)
remove(W2W3_geordi)

W2W3_geordi.usersummary <- W2W3_geordi.m %>%
  select(user_id,status,action) %>%
  group_by(user_id,status,action) %>%
  tally()

W3W4_geordi <- fread("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W3W4/ConcatSequenceW3W4.csv")

W3W4_geordi.m <- reshape2::melt(W3W4_geordi[-1,], id = c("V1","V2")) 
W3W4_geordi.m <- W3W4_geordi.m[which(W3W4_geordi.m$value !="0"),]
names(W3W4_geordi.m) <- c("user_id","status","order","action") 
W3W4_geordi.m$order <- gsub("V","",W3W4_geordi.m$order)
remove(W3W4_geordi)

W3W4_geordi.usersummary <- W3W4_geordi.m %>%
  select(user_id,status,action) %>%
  group_by(user_id,status,action) %>%
  tally()

W4W5_geordi <- fread("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W4W5/ConcatSequenceW4W5.csv")

W4W5_geordi.m <- reshape2::melt(W4W5_geordi[-1,], id = c("V1","V2")) 
W4W5_geordi.m <- W4W5_geordi.m[which(W4W5_geordi.m$value !="0"),]
names(W4W5_geordi.m) <- c("user_id","status","order","action") 
W4W5_geordi.m$order <- gsub("V","",W4W5_geordi.m$order)
remove(W4W5_geordi)

W4W5_geordi.usersummary <- W4W5_geordi.m %>%
  select(user_id,status,action) %>%
  group_by(user_id,status,action) %>%
  tally()

#### IMPORT GEORDI 
geordi_coded <- fread("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/geordi/events-coded.csv")

geordi_complete <- fread("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/geordi/geordi.csv")
geordi_1_5_17 <- fread("~/Downloads/geordi-1-5-17.csv")

#### IMPORT COMMENTS 
comments <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/cscw-analysis/comments/gravity-spy-comments_2019-07-26.csv")
#### IMPORT PERFORMANCE DATA FROM CLASSIFICATIONS
user_performance <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/cscw-analysis/user_performance.csv")

```

