---
title: "Analysis of User SubSequences "
author: "Corey Jackson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(tabula)
library(gtsummary)

userW1W2 <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W1W2/Subsequences_Count_W1W2.csv")

userW1W2 <- userW1W2[,-1]

userW1W2 <- userW1W2 %>%
  mutate(total_subsequeces = rowSums(.[1:21])) %>%
  rowwise() %>% 
  mutate(unique_subsequeces = 21- sum(c_across(1:21) == 0))
  
# Measure diversity of activities 
## https://cran.r-project.org/web/packages/tabula/vignettes/diversity.html 
userW1W2 <- data.frame(userW1W2)
userW1W2$Status2 <- ifelse(userW1W2$Status=="Promoted",1,0)

userW1W2$richness <- as.numeric(richness(userW1W2[1:21], method = "margalef")) 
userW1W2_richness <- na.omit(userW1W2) 
wilcox.test(userW1W2_richness$richness,userW1W2_richness$Status2)

userW1W2$rarefaction <- as.numeric(composition(userW1W2[1:21], method = "chao1")) 
userW1W2_rarefaction <- na.omit(userW1W2) 
wilcox.test(userW1W2_rarefaction$rarefaction,userW1W2_rarefaction$Status2)

userW1W2$workflow <- "W1W2"
##################################################################

userW2W3 <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W2W3/Subsequences_Count_W2W3.csv")

userW2W3 <- userW2W3[,-1]

userW2W3 <- userW2W3 %>%
  mutate(total_subsequeces = rowSums(.[1:42])) %>%
  rowwise() %>% 
  mutate(unique_subsequeces = 42 - sum(c_across(1:42) == 0))

userW2W3 <- data.frame(userW2W3)
userW2W3$Status2 <- ifelse(userW2W3$Status=="Promoted",1,0)

userW2W3$richness <- as.numeric(richness(userW2W3[1:42], method = "margalef")) 
userW2W3_richness <- na.omit(userW2W3) 
wilcox.test(userW2W3_richness$richness,userW2W3_richness$Status2)

userW2W3$rarefaction <- as.numeric(composition(userW2W3[1:42], method = "chao1")) 
userW2W3_rarefaction <- na.omit(userW2W3) 
wilcox.test(userW2W3_rarefaction$rarefaction,userW2W3_rarefaction$Status2)

userW2W3$workflow <- "W2W3"
##################################################################

userW3W4 <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W3W4/Subsequences_Count_W3W4.csv")

userW3W4 <- userW3W4[,-1]

userW3W4 <- userW3W4 %>%
  mutate(total_subsequeces = rowSums(.[1:299])) %>%
  rowwise() %>% 
  mutate(unique_subsequeces = 299 - sum(c_across(1:299) == 0))

userW3W4 <- data.frame(userW3W4)
userW3W4$Status2 <- ifelse(userW3W4$Status=="Promoted",1,0)


userW3W4$richness <- as.numeric(richness(userW3W4[1:299], method = "margalef")) 
userW3W4_richness <- na.omit(userW3W4) 
wilcox.test(userW3W4_richness$richness,userW3W4_richness$Status2)

userW3W4$rarefaction <- as.numeric(composition(userW3W4[1:299], method = "chao1")) 
userW3W4_rarefaction <- na.omit(userW3W4) 
wilcox.test(userW3W4_rarefaction$rarefaction,userW3W4_rarefaction$Status2)

userW3W4$workflow <- "W3W4"


##################################################################
userW4W5 <- read_csv("~/Library/CloudStorage/Box-Box/_research/traceGA/motif[collab]/data/SequenceBetweenLevels/W4W5/Pt2_Threshold/Subsequences_Count_W4W5.csv")

userW4W5 <- userW4W5[,-1]

userW4W5 <- userW4W5 %>%
  mutate(total_subsequeces = rowSums(.[1:256])) %>%
  rowwise() %>%
  mutate(unique_subsequeces = 256 - sum(c_across(1:256) == 0))

userW4W5 <- data.frame(userW4W5)
userW4W5$Status2 <- ifelse(userW4W5$Status=="Promoted",1,0)


userW4W5$richness <- as.numeric(richness(userW4W5[1:256], method = "margalef"))
userW4W5_richness <- na.omit(userW4W5)
wilcox.test(userW4W5_richness$richness,userW4W5_richness$Status2)

userW4W5$rarefaction <- as.numeric(composition(userW4W5[1:256], method = "chao1"))
userW4W5_rarefaction <- na.omit(userW4W5)
wilcox.test(userW4W5_rarefaction$rarefaction,userW4W5_rarefaction$Status2)

userW4W5$workflow <- "W4W5"

### COMBINE

userworkflows <- rbind(userW1W2[,c(22:29)],userW2W3[,c(43:50)],userW3W4[,c(300:307)],userW4W5[257:264])
#userworkflows <- rbind(userW1W2[,c(22:29)],userW2W3[,c(43:50)],userW3W4[,c(300:307)])

userworkflows_differences <- na.omit(userworkflows)

#Compute change in richness and rarefaction
userworkflows <- userworkflows %>%
    arrange(desc(user),workflow) %>%
    group_by(user) %>%
    mutate(diff_richness = richness - lag(richness),
           diff_rarefaction = rarefaction - lag(rarefaction)
           )


W1W2_summary <-  userworkflows[,c(1,3,4,6,7,8)] %>%
  filter(workflow=="W1W2") %>%
  select(-workflow) %>%
  tbl_summary(by = Status, 
  statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>% 
  add_p()

W2W3_summary <-  userworkflows[,c(1,3,4,6,7,8)] %>%
  filter(workflow=="W2W3") %>%
  select(-workflow) %>%
  tbl_summary(by = Status, 
    statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%   add_p()

W3W4_summary <-  userworkflows[,c(1,3,4,6,7,8)] %>%
  filter(workflow=="W3W4") %>%
  select(-workflow) %>%
  tbl_summary(by = Status, 
   statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%   add_p()

W4W5_summary <-  userworkflows[,c(1,3,4,6,7,8)] %>%
  filter(workflow=="W4W5") %>%
  select(-workflow) %>%
  tbl_summary(by = Status,
   statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%   add_p()

### DIfFERENCES
userworkflows_differences <- na.omit(userworkflows)

W2W3_diff <-  userworkflows_differences[,c(1,8:10)] %>%
  filter(workflow=="W2W3") %>%
  select(-workflow) %>%
 tbl_summary(by = Status, 
  statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%  
  add_p()

W3W4_diff <-  userworkflows_differences[,c(1,8:10)] %>%
  filter(workflow=="W3W4") %>%
  select(-workflow) %>%
  tbl_summary(by = Status, 
  statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%
  add_p()

W4W5_diff <-  userworkflows_differences[,c(1,8:10)] %>%
  filter(workflow=="W4W5") %>%
  select(-workflow) %>%
  tbl_summary(by = Status,
  statistic = list(
      all_continuous() ~ "{mean} ({sd},{median})",
      all_categorical() ~ "{n} / {N} ({p}%)"
    )) %>%
  add_p()
```

The higher the number of sequences present, the higher the sequence richness.

## Sequence Richness

The higher the number of sequences present, the higher the sequence richness.

## Sequence Rarefaction

A statistical technique used to compare the sequence richness of different samples that have been collected from different areas or at different times. It is used to estimate the expected number of sequence in a sample of a given size, based on the number of sequence found in a larger sample size. Rarefaction is a tool used to compare the relative richness of different samples, and to estimate the expected number of sequences in a smaller sample size

```{r}
W1W2_summary

W2W3_summary

W3W4_summary

W4W5_summary
```

### Changes in richness and rarefaction

```{r}
W2W3_diff

W3W4_diff

W4W5_diff

```

